### 2012-03-25 exam4/2.tex
problem 1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{./exam}
\usepackage{type1cm} % We are using scalable fonts. Really.
\usepackage{alltt,times,comment,amsmath}
\usepackage{alltt}
\usepackage{ct} % tight CM font for \tt
\usepackage[usenames,dvipsnames]{xcolor}
\newexercise{exercise}{Exercise}[subsection]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\vspace*{-1.5cm}
\centerline{\Large CSU2510H Exam 1 \ifrubric (SOLUTION) \fi-- Spring 2012}

@@

% \noindent
% {\bf Home on the Range}

% Come up with funny story here.

% \newpage
\begin{problem}\pts{18} % same as on the previous exam :)

Here is a data definition for a class of objects.  It intentionally
uses meaningless names to test whether you've sufficiently
internalized the data-driven development process we've talked about
since the Fall.

\begin{verbatim}
;; A P is one of:          
;; - A                  ;; An A is a (new a% String)
;; - B                  ;; A  B is a (new b% String A)
;; - C                  ;; A  C is a (new c% P)

(define-class a% (fields w))
(define-class b% (fields x y))
(define-class c% (fields z))
\end{verbatim}

\noindent
Design the following methods for \verb|P|s:

@@

\item \verb|size| - the size of an \verb|A| is $5$; the size of a
  \verb|B| is $8$, regardless of what's inside; and the size of a
  \verb|C| contributes $1$ to the size of the \verb|P| inside.

\item \verb|replace-x| - produces a \verb|P| like this one, but
  with any \verb|x| field replaced by the given string.

\item \verb|same-x-and-w?| - given two strings, produce true if this
  \verb|P| contains a \verb|B| whose \verb|x| is equal to the
  first given string and whose \verb|y| is an \verb|A| whose
  \verb|w| is equal to the second given string.  Produces false
  otherwise.

@@

Be sure to define any interfaces you need and say which classes
implement which interfaces so that your program treats all values
according to their interface.

@@

\begin{solution}
\begin{alltt}
\rubricpts{6 pts -- contract and purpose for each method}
;; A P implements:
;; - size : -> Number
;;   Size of this P.
;; - replace-x : String -> P
;;   Replace x field (if any) of this P with given string.
;; - same-x-and-w? : String String -> Boolean
;;   Is there a B within this P with given x field and w field?

\rubricpts{0 pts -- not required, but write something}
;; An A implements:
;; - w : -> String
;;   Get the w string.

\rubricpts{2 pts}
;; In a%: 
(define (size) 5)
(define (replace-x str) this)
(define (same-x-and-w? g c) false)

\rubricpts{3 pts}
;; In b%:
(define (size) 8)
(define (replace-x str)
  (new b% str (this . y)))
(define (same-x-and-w? g c)
  (and (string=? g (this . x))
       (string=? c (this . y . w))))

\rubricpts{4 pts}
;; In c%:
(define (size) (add1 (this . z . size)))
(define (replace-x str)
  (new c% (this . z . replace-x str)))
(define (same-x-and-w? g c)
  (this . z . same-x-and-w? g c))

;; tests
\rubricpts{3 pts -- 1 per method}
(define a (new a% "a"))
(define b (new b% "b" a))
(define c (new c% b))
(define d (new c% a))
(check-expect (a . size) 5)
(check-expect (b . size) 8)
(check-expect (c . size) 6)
(check-expect (d . size) 9)
(check-expect (a . replace-x "*") a)
(check-expect (b . replace-x "*") (new b% "*" a))
(check-expect (c . replace-x "*") (new c% (new b% "*" a)))
(check-expect (d . replace-x "*") d)
(check-expect (a . same-x-and-w? "b" "a") false)
(check-expect (b . same-x-and-w? "b" "a") true)
(check-expect (c . same-x-and-w? "b" "a") true)
(check-expect (d . same-x-and-w? "b" "a") false)
\end{alltt}
\end{solution}
\end{problem}
%\ifrubric\bigskip\else
\newpage
%\fi

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{tikz} 
\usepackage{qtree} 
\usepackage{./exam}
\usepackage{type1cm} % We are using scalable fonts. Really.
\usepackage{alltt,times,comment,amsmath}
\usepackage{alltt}
\usepackage{ct} % tight CM font for \tt
\usepackage{xcolor}
\newexercise{exercise}{Exercise}[subsection]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\vspace*{-1.5cm}
\centerline{\Large CSU2510H Exam 2 \ifrubric (SOLUTION) \fi-- Spring 2012}

@@

\begin{problem}\pts{18} % same as on the previous exam :)

  While trying to manage the grade database, Asumu hit upon a new idea
  for a data structure: the 2/3-tree.  A 2/3-tree is either a leaf
  (which holds a {\tt String} value), a 2-node, or a 3-node.  A 2-node
  has two children, and a 3-node has three children.  The twist is
  that a 2-node can't have any 2-nodes as children, and a 3-node can't
  have any 3-nodes as children.

Here's an example of a 2/3-tree:

\vspace*{8mm}
\bigskip

\Tree [. {\tt "Cat"} {\tt "Hat"} [. {\tt "Zebra"} {\tt "Rhino"}  ] !{\qbalance} ]

\bigskip
\bigskip

@@

\item Design data, class, and interface definitions, in Java, to
  represent 2/3-trees.  Construct the above example using your
  definitions.

\item Design the {\tt height} method, which computes the height of the
  tree (i.e., the maximum distance from the root to a leaf).  The
  example tree has a height of 3.

@@

@@

\begin{solution}
\begin{alltt}
\rubricpts{? pts}
\end{alltt}
\end{solution}
\end{problem}
%\ifrubric\bigskip\else
\newpage
%\fi
